Demes: a standard format for demographic models

### 2022-08-08 paper.tex
Fix build and trim MSMC text

% local definitions
\newcommand{\ms}[0]{\texttt{ms}}
\newcommand{\msprime}[0]{\texttt{msprime}}
\newcommand{\stdpopsim}[0]{\texttt{stdpopsim}}
\newcommand{\demes}[0]{\texttt{demes}}
\newcommand{\demesdraw}[0]{\texttt{demesdraw}}
\newcommand{\Demes}[0]{\texttt{Demes}}
\newcommand{\moments}[0]{\texttt{moments}}
\newcommand{\dadi}[0]{\texttt{dadi}}
\newcommand{\fwdpy}[0]{\texttt{fwdpy11}}
\newcommand{\slim}[0]{\texttt{SLiM}}
\newcommand{\gadma}[0]{\texttt{GADMA}}
\newcommand{\tskit}[0]{\texttt{tskit}}
\newcommand{\demesslim}[0]{\texttt{demes-slim}}

@@

\affil[1]{Section for Molecular Ecology and Evolution, Globe Institute, University of Copenhagen}
\affil[2]{Department of Integrative Biology, University of Wisconsin--Madison}
\affil[3]{Department of Molecular and Cellular Biology, University of Arizona}
\affil[4]{Institute of Ecology and Evolution, The University of Edinburgh}
\affil[5]{Computer Technologies Laboratory, ITMO University}
\affil[6]{Big Data Institute, Li Ka Shing Centre for Health Information and
    Discovery, University of Oxford}
\affil[7]{Ecology and Evolutionary Biology, University of California, Irvine}
\affil[8]{Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}

@@

These basic assumptions of discrete Wright-Fisher populations connected by
instantaneous or continuous
migrations are shared by many inference methods
\citep[e.g.,][]{gutenkunst2009inferring,li2011inference,
gravel2012population,kamm2017efficient,
jouganous2017inferring,ragsdale2019models,
excoffier2021fastsimcoal2}, and
forwards- and backwards-time simulators~\citep[e.g.,][]{hudson2002generating,
gutenkunst2009inferring,
excoffier2011fastsimcoal,kelleher2016efficient,
jouganous2017inferring,haller2019slim,thornton2019-nu}.
Demes therefore serves as ``middleware'' between inference methods and simulation
software, capturing these common assumptions.

>>>>

% local definitions
\newcommand{\ms}[0]{\texttt{ms}}
\newcommand{\msprime}[0]{\texttt{msprime}}
\newcommand{\stdpopsim}[0]{\texttt{stdpopsim}}
\newcommand{\demes}[0]{\texttt{demes}}
\newcommand{\demesdraw}[0]{\texttt{demesdraw}}
\newcommand{\Demes}[0]{\texttt{Demes}}
\newcommand{\moments}[0]{\texttt{moments}}
\newcommand{\dadi}[0]{\texttt{dadi}}
\newcommand{\fwdpy}[0]{\texttt{fwdpy11}}
\newcommand{\slim}[0]{\texttt{SLiM}}
\newcommand{\gadma}[0]{\texttt{GADMA}}
\newcommand{\tskit}[0]{\texttt{tskit}}
\newcommand{\MSMC}[0]{\texttt{MSMC}}
\newcommand{\demesslim}[0]{\texttt{demes-slim}}

@@

\affil[1]{Section for Molecular Ecology and Evolution, Globe Institute, University of Copenhagen}
\affil[2]{Department of Integrative Biology, University of Wisconsin--Madison}
\affil[3]{Department of Molecular and Cellular Biology, University of Arizona}
\affil[4]{Institute of Ecology and Evolution, The University of Edinburgh}
\affil[5]{Computer Technologies Laboratory, ITMO University}
\affil[6]{Big Data Institute, Li Ka Shing Centre for Health Information and
    Discovery, University of Oxford}
\affil[7]{Ecology and Evolutionary Biology, University of California at Irvine}
\affil[8]{Max Planck Institute for Evolutionary Anthropology, Leipzig, Germany}

@@

These basic assumptions of discrete Wright-Fisher populations connected by
instantaneous or continuous
migrations are shared by many inference methods
\citep[e.g.,][]{gutenkunst2009inferring,li2011inference,
gravel2012population,
SchiffelsDurbin2014,
kamm2017efficient,
jouganous2017inferring,ragsdale2019models,
excoffier2021fastsimcoal2}, and
forwards- and backwards-time simulators~\citep[e.g.,][]{hudson2002generating,
gutenkunst2009inferring,
excoffier2011fastsimcoal,kelleher2016efficient,
jouganous2017inferring,haller2019slim,thornton2019-nu}.
Demes therefore serves as ``middleware'' between inference methods and simulation
software, capturing these common assumptions.
